### 2021-01-27 README.Rmd

#### 1. rob_summary()
Returns a ggplot object displaying a barchart of the risk of bias of included studies across the domains of the specified tool. [*Note: the defaults used in this function have changed from their original settings, so that a un-weighted barplot is now produced by default. See the NEWS.md file for further information.*]

@@

>>>>

#### 1. rob_summary()
Returns a ggplot object displaying a bar-chart of the risk of bias of included studies across the domains of the specified tool. [*Note: the defaults used in this function have changed from their original settings, so that a un-weighted barplot is now produced by default. See the NEWS.md file for further information.*]

@@

``` {r, echo = FALSE}
plot <- rob_summary(data = data_rob2, tool = "ROB2", overall = FALSE)
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
